Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-01 manuscript/coverletter_resub.tex
coverletter looks good enough to send to co-authors

		Plants' interactions with animals can significantly affect their fitness, both positively and negatively. These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge. The question of whether, and how strongly, plants' interaction partners are phylogenetically conserved has excited continuing interest, as it is likely an important step towards understanding the eco-evolutionary dynamics of plant-insect communities. Within this context, our work takes one step beyond considering whole-network trends to examine variation between plant families. We believe that this finer-grained approach will be critical in future efforts to find the mechanisms driving conservationof interaction partners.

		We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology). Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently. Nevertheless, we respect their prior publication and have taken care to refer to it in our manuscript. Our manuscript does, however, include a few methodological innovations which greatly add to its novelty. First, we define overlap in interaction partners using numbers of shared and not-shared partners (analogous to numbers of successes and failures in Bernoulli trials). This approach, as opposed to using only the number or propotion of shared interaction partners, effectively weights our data according to how much information is available and appears to be a more powerful tool to detect weak trends. Second, in addition to overall trends at the network level, we also test whether these trends are related to community composition and whether different plant families show different trends. These more-detailed analyses complement the usual network-level approach to give more insight into potential drivers of conservation of interaction partners. We believe that these additions to our methodology are enough to distinguish our work from that of Fontaine \& Th\'{e}bault. ]]

>>>>

		Plants' interactions with animals can significantly affect their fitness, both positively and negatively. These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be conserved if there is selection to avoid overlap with close relatives or if distant relatives converge. The question of whether, and how strongly, plants' interaction partners are phylogenetically conserved has excited continuing interest, as it is likely an important step towards understanding the eco-evolutionary dynamics of plant-insect communities. Within this context, our work takes one step beyond considering whole-network trends to examine variation between plant families. We believe that this finer-grained approach will be critical in future efforts to find the mechanisms driving conservationof interaction partners.

		\indent We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology). Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently. Nevertheless, we respect their prior publication and have taken care to refer to it in our manuscript. Our manuscript does, however, include a few methodological innovations which greatly add to its novelty. First, we define overlap in interaction partners using numbers of shared and not-shared partners (analogous to numbers of successes and failures in Bernoulli trials). This approach, as opposed to using only the number or propotion of shared interaction partners, effectively weights our data according to how much information is available and appears to be a more powerful tool to detect weak trends. Second, in addition to overall trends at the network level, we also test whether these trends are related to community composition and whether different plant families show different trends. These more-detailed analyses complement the usual network-level approach to give more insight into potential drivers of conservation of interaction partners. We believe that these additions to our methodology are enough to distinguish our work from that of Fontaine \& Th\'{e}bault.
